Project Uccle

### 2020-06-06 project.Rmd
add composed weekly seasonality figure

plot_grid(
  autoplot(aggregated) + labs(title="Timeseries", cex=0.7) + ylab("") + xlab("") + theme(plot.margin=margin(b=-6, unit="pt")),
  autoplot(ts(season.24$figure, frequency=1)) + labs(title="Daily seasonality", cex=0.7) + ylab("") + xlab("") + theme(plot.margin=margin(r=10, b=-6, unit="pt")),
  autoplot(ts(season.168$trend, frequency=168)) + labs(title="Trend", cex=0.7) + ylab("") + xlab("") + theme(plot.margin=margin(l=4, b=-6, unit="pt")),
  autoplot(ts(season.168$figure, frequency=1)) + labs(title="Weekly seasonality", cex=0.7) + ylab("") + xlab("") + theme(plot.margin=margin(r=10, b=-6, unit="pt")),
  autoplot(aggregated-season.24$seasonal-season.168$seasonal-season.168$trend) + labs(title="Residuals", cex=0.7) + ylab("") + xlab("") + theme(plot.margin=margin(t=-6, b=-6, unit="pt")),
  nrow = 3,
  greedy = T)

>>>>

plot_grid(
  autoplot(aggregated) + labs(title="Timeseries", cex=0.7) + ylab("") + xlab("") + theme(plot.margin=margin(b=-6, unit="pt")),
  autoplot(ts(season.24$figure, frequency=1)) + labs(title="Daily seasonality", cex=0.7) + ylab("") + xlab("") + theme(plot.margin=margin(r=10, b=-6, unit="pt")),
  autoplot(ts(season.168$trend, frequency=168)) + labs(title="Trend", cex=0.7) + ylab("") + xlab("") + theme(plot.margin=margin(l=4, b=-6, unit="pt")),
  autoplot(ts(season.168$figure, frequency=1)) + labs(title="Weekly seasonality", cex=0.7) + ylab("") + xlab("") + theme(plot.margin=margin(r=10, b=-6, unit="pt")),
  autoplot(aggregated-season.24$seasonal-season.168$seasonal-season.168$trend) + labs(title="Residuals", cex=0.7) + ylab("") + xlab("") + theme(plot.margin=margin(t=-6, b=-6, unit="pt")),
  autoplot(season.168$figure + rep(season.24$figure, 7)) + labs(title="Weekly seasonality (sum)", cex=0.7) + ylab("") + xlab("") + theme(plot.margin=margin(r=10, b=-6, unit="pt")),
  nrow = 3,
  greedy = T)
